---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(emojiscape)
set.seed(1337)
```

# {emojiscape}

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

{emojiscape} is a tiny R package that prints to the console a randomised emoji scene. Choose a terrain and three emoji of that theme will be sampled with different probabilities and rendered to a grid size of your choosing.

## Install

Install {emojiscape} from GitHub. It requires [the GitHub-hosted {emo} package](https://github.com/hadley/emo), which is built on [emojilib](https://github.com/muan/emojilib/).

```{r eval=FALSE}
remotes::install_github("matt-dray/emojiscape")
```

No guarantees. I've tested it only on my own macOS machine.

## Build a tiny world

Let's `generate()` a scene. There are several `terrain` options to try (yes, there is `liminal`).

```{r terrrain-set, echo=FALSE}
paste(as.list(args(generate))$terrain)[-1]
```

Here's some `woods`. What a _hoot_.

```{r woods}
emojiscape::generate(terrain = "woods")
```

Hold your breath, we're going to `space`. You can resize the output, but space is basically infinite and my console is not.

```{r space}
emojiscape::generate("space", grid_size = 7)
```

Here's a little raccoon `city`. Perhaps the _residents_ are _evil_? (That is a gamer joke, gg.)

```{r city}
emojiscape::generate("city", 5)
```

## Tune the frequencies

Use `get_set()` to see each terrain's emoji set and their 'suggested frequency' slot.

```{r mountains-emoji}
emojiscape::get_set("mountains")
```

But you can totally mess with the probablities for these in `generate()`.

Any _The Mountain Goats_ fans?

```{r mountains}
emojiscape::generate(
  "mountains",
  prob_common = 0.1,
  prob_uncommon = 0.2,
  prob_rare = 0.7  # INCREASE GOAT FREQUENCY
)
```

